\documentclass[11pt, letterpaper]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{bold-extra}
\usepackage{enumitem}
\usepackage{multicol}   % multiple columns
\usepackage[T1]{fontenc}
\usepackage{stix2}     % default font
\usepackage{lipsum}

% remove page numbering
\pagenumbering{gobble}      

\titleformat{\section}
{\scshape\large}{}{0em}
{}[\titlerule]
\titlespacing{\section}{0pt}{13pt}{8pt}

\titleformat{\subsection}
{\bfseries}{}{0em}
{}
\titlespacing{\subsection}{0pt}{8pt}{0pt}

\newenvironment{nitemize}{%
  \begin{itemize}[label={},topsep=0pt,itemsep=0pt,parsep=0pt,leftmargin=*]%
}{%
  \end{itemize}%
}

\begin{document}
\begin{multicols}{2}
% ==================== HEADER ====================
\begin{flushleft}
    \textbf{\Large Jinseob Sohn}\hfill \textbf{jsohn@colgate.edu} \\
        Box V 5191, 13 Oak Drive \hfill +1 (315) 273-9562 \\
        Hamilton, NY 13346 \hfill +82 10-2527-3832 \\
\end{flushleft}

    
% ==================== EDUCATION ====================
\section{Education}
\subsection{Colgate University} 
\noindent Hamilton, New York, USA \hfill Sep 2017 – May 2023\\
\textit{Bachelor of Arts}, Cumulative GPA: 3.74/4.00\\
Major/Minor: Computer Science/Mathematics
\subsection{KOABELS American Law Institute} 
\noindent Gangnam, Seoul, South Korea \hfill Mar 2020 – \textit{present} \\
\textit{Pre-Law Programme}

% ==================== OTHER SKILLS ====================
\section{Skills}
\noindent \textbf{Programming Languages:} \emph{Python}, \emph{Java}, \emph{C}, MIPS Assembly, ARM Assembly, \LaTeX, JavaScript\\
\noindent \textbf{Operating Systems:} \emph{macOS}, \emph{Debian/Ubuntu Linux}, \emph{Arch Linux}, \emph{Manjaro}, Windows 10/11\\
\textbf{Software: } \emph{Git}, \emph{ViM}, \emph{VSCode}, \emph{Microsoft Excel}, Word, PowerPoint,  WordPress, \emph{ArcGIS Pro}, \emph{Adobe Photoshop}, \emph{Final Cut Pro X}\\
\textbf{Spoken Languages:} \emph{English}, \emph{Korean}, \emph{French}, German
% ==================== EXPERIENCE ====================
\section{Experience}
\subsection{Introduction to Computing Systems Lab TA}
\noindent \emph{Department of Computer Science} \hfill Jan 2023 – May 2023\\
I worked as a Teaching Assistant for a 200-level computer architecture class, teaching the fundamentals of computer architecture and hardware through assembly language and C.
\begin{nitemize}
    \item \(\bullet\) Course Code: COSC 208
    \item \(\bullet\) Required Skills: Ubuntu/Linux, ARM Assembly, C
\end{nitemize}
\subsection{Introduction to Computing Lab TA}
\noindent \emph{Department of Computer Science} \hfill Aug 2022 – Dec 2022\\
I worked as a Teaching Assistant for a 100-level introductory course, teaching the basics of computer programming languages and algorithmic thinking. I worked during laboratory hours where students were expected to apply the skills they learned during lectures.
\begin{nitemize}
    \item \(\bullet\) Courses: COSC 101, 102
    \item \(\bullet\) Required Skills: Python, Java, OOP
\end{nitemize}

\subsection{DELF French Language Tutor}
\noindent \emph{Self-Employed} \hfill Jan 2020 – Jan 2021\\
Worked as a language tutor in South Korea for students studying for the DELF (Diplôme d’études en langue française, French language proficiency test) Level B2 certification exam.
\begin{nitemize}
    \item \(\bullet\) Certification: DELF B2 (Cred. ID: 082002-032498)
\end{nitemize}

\section{Volunteering}
\subsection{Colgate University Orchestra} 
\noindent \emph{Department of Music} \hfill Sep 2017 – May 2018\\
\noindent I served as a pianist and violinist with the Colgate Chamber Players, a university-based chamber music group. Played as a group in regularly scheduled public recitals in both Hamilton and on campus.

\subsection{Colgate Chamber Players} 
\noindent \emph{Department of Music} \hfill Sep 2017 – May 2018\\
\noindent Served at the University Orchestra as a member of the 2nd Violin section. Took part in semesterly recitals and concerts.

\subsection{Colgate University Piano Club} 
\noindent \emph{Extracurricular} \hfill Jan 2018 – May 2018\\
I served as the Treasurer of the Colgate Piano Club for Spring 2018. I was responsible for allocating budgets for concerts from visiting artists and controlling expenses.
% ==================== AWARDS ====================
\section{Awards}
\noindent\textbf{Dean's Award with Distinction} \hfill Fall 2017/21/22, Spring 2018/21\\
Issued by Colgate University for students who achieved a 3.6 or higher GPA with a minimum of 3.75 academic credits.

\noindent\textbf{Dean's Award for Academic Excellence} \hfill Fall 2018\\
Issued by Colgate University for students who achieved a 3.3 or higher GPA with a minimum of 3.75 academic credits.

\noindent\textbf{Alumni Memorial Scholar} \hfill Fall 2017\\
Awarded by Colgate University to top applicants in incoming class.

\end{multicols}
\end{document}